### 2023-04-22 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

\chapter{O que ficou para depois}

Inclua aqui informações que não sejam tão relevantes para o entendimento do projeto mas que ainda sejam importantes para documentá-lo.

put here the stability difficult about doing experiments

- syringe pump inclined
- pumping liquid to avoid bubbles
- mechanical noise in the pumping machine
- external electrical noise collected by antennas or connections

>>>>

\chapter{Trials and failures}

\section{Machine Learn}

I've tried to create a database with the samples of current. Each sample was a vector with 50k values corresponding a 0.5s of data collected in a 100KHz oscilloscope. And in a second column its

\subsection{Spectogram analysis}

### 2023-04-22 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

>>>>

The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
The previous student work was more focused on detecting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
From the work I've done it highlights:

- Integrate liquid pump to the software and developed a routine with it.

- Modeled the software to fit a control model turning it easy to implement new control algorithms or experiment routines.

- Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.

- Developed a classification for multi jet spraying mode.

- Developed a simple controller to proof the concept.

- Optimize the saving of data to a real time streaming together with more sensors' data.

- Restructured algorithm usability in order to make it more intuitive with the setup file.

### 2023-04-22 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.

About the activities made to reach our goals, it highlights the following:

- Integrate high speed camera and liquid pump to the peripherals connected to the software.

- Develop of a control model to automatic stabilize the electrospraying mode.

- Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.

- Reduce the data collected size and optimize the saving to a real time streamming.

- Develop new automatic experiment routines such as mapping and control routines.

- Reestructure the setup file and the algorithm usability in order to make it more intuitive.

- Integration with many computer architectures to be able to run in a portable computer such as a \emph{Raspberry Pi}.

    \begin{figure}[H]
        \centering
        \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
        \caption{EHDA automation system setup}
        \label{fig:metodology_example1}
    \end{figure}

\section{System Model}
\label{sec:control_model}

ilustramos o processo com a Figura \ref{fig:control_model_fig}.

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
  \caption{EHDA automation system setup}
  \label{fig:control_model_fig}
\end{figure}

\subsection{Threading and Queues}
\label{subsec:concurrency}

    In order to implement this system model to the software and explore parallel processing each system in the
    model was developed as a separate Thread.
    For cuncurrency on flux of data between threads was used queues structures.
    A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.

    \subsection{Controller Thread}

        It is responsible of sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
        Also responsible of sending the finish event command that end the routine and trigger the threads to close their routines.
        As input we have the setup config file and the \emph{feedback\_queue}. As output we have the values in the emph{controller\_output\_queue()}.

    \subsection{Data Acquisition Thread}
    \label{subsec:data_aquisition}

        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the powersupply, flowrate from the pump and concatenate into one sample data.
        As output we have the values in the emph{data\_queue()}.

    \subsection{Data Processing Thread}

        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
        As output we have the values in the emph{save\_data\_queue()}, emph{plotting\_queue()} and emph{feedback\_queue()}.

        \subsection{Save Data Thread}

        After the processing the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.

        With the new streamming model of saving a new structure of the collected data were created.
        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
        The structure of the

        \begin{figure}[H]
            \center
            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
            \caption{Output data json structure}
        \end{figure}

        To work with this data I'm using pandas Dataframe.
        With the command:

        pandas.read\_json('PATH', orient='index').

        The json file is good to store the data and to read the file. But as it is getting a lot of data working with pandas Dataframe is being way faster. Also saving the dataframe in a compressed
        type of file called feather is much faster to work with the data.

    \subsection{Video Thread}

        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.

    \subsection{Plot}

        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilites of running outside of the main function. 
        It is responsible of plotting in real time the current sample acquired and it respective fast fourier transform to evaluate the sample frequency spectrum.

    - plotting data queue

@@

@@

>>>>

@@

To classify the multijet I searched \cite{Ryan} The data thus obtained shows that in all cases the relationship between current and flow rate observed in single cone-jet mode is maintained in multi-jet mode when the current and flow rate is normalized by the number of jets.

@@

For the machine learning

### 2023-04-22 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

\section{Instrumentation}
\label{sec:instrumentation}

@@

    The iterface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}. Note that is also important to have the \emph{printinfo.py} file in the project folder in order to work.

@@

\section{Setup Validation}
\label{sec:setup_validation}

@@

>>>>

This chapter is about to describe the equipment used and its integration explaining how it was modeled and implemented in both hardware and software sides.

\section{System Description}
\label{sec:system_description}

\subsection{Instrumentation}
\label{subsec:instrumentation}

@@

    The interface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}. Note that is also important to have the \emph{printinfo.py} file in the project folder in order to work.

@@

\subsection{Setup Validation}
\label{subsec:setup_validation}

@@

    \begin{figure}[H]
        \centering
        \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
        \caption{EHDA automation system setup}
        \label{fig:metodology_example1}
    \end{figure}

\section{System Model}
\label{sec:control_model}

ilustramos o processo com a Figura \ref{fig:control_model_fig}.

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
  \caption{EHDA automation system setup}
  \label{fig:control_model_fig}
\end{figure}

\subsection{Threading and Queues}
\label{subsec:concurrency}

    In order to implement this system model to the software and explore parallel processing each system in the
    model was developed as a separate Thread.
    For cuncurrency on flux of data between threads was used queues structures.
    A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.

    \subsection{Controller Thread}

        It is responsible of sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
        Also responsible of sending the finish event command that end the routine and trigger the threads to close their routines.
        As input we have the setup config file and the \emph{feedback\_queue}. As output we have the values in the emph{controller\_output\_queue()}.

    \subsection{Data Acquisition Thread}
    \label{subsec:data_aquisition}

        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the powersupply, flowrate from the pump and concatenate into one sample data.
        As output we have the values in the emph{data\_queue()}.

    \subsection{Data Processing Thread}

        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
        As output we have the values in the emph{save\_data\_queue()}, emph{plotting\_queue()} and emph{feedback\_queue()}.

        \subsection{Save Data Thread}

        After the processing the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.

        With the new streamming model of saving a new structure of the collected data were created.
        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
        The structure of the

        \begin{figure}[H]
            \center
            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
            \caption{Output data json structure}
        \end{figure}

        To work with this data I'm using pandas Dataframe.
        With the command:

        pandas.read\_json('PATH', orient='index').

        The json file is good to store the data and to read the file. But as it is getting a lot of data working with pandas Dataframe is being way faster. Also saving the dataframe in a compressed
        type of file called feather is much faster to work with the data.

    \subsection{Video Thread}

        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.

    \subsection{Plot}

        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilites of running outside of the main function. 
        It is responsible of plotting in real time the current sample acquired and it respective fast fourier transform to evaluate the sample frequency spectrum.

    - plotting data queue
